SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-07 docs/questioning.tex
add Nature reference for code sharing

>>>>

To ensure replicability of research results the source code
implementing a detection mechanism should be available to researchers.
Ideally the code should be available under an open source license, so
that it is easy to modify and improve an approach; even when this is
not possible, for whatever reason, it is important to make sure that
all computer code and test data is available noting any restrictions
on accessibility. Availability of computer code has been recognised as
an important issue outside the computer science field: the journal
Nature, in a recent editorial, adopted a publication policy stressing
access to code and data~\cite{nature2014}. At a time and date that the
merits of open access to code are discussed in non computer science
journals~\cite{easterbrook2014} we should expect computer scientists
to lead the way.
